\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{PARTHA DEY} \\
 % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{Master of Computer Applications, 2025 \\ (+91) 9062681888 \\ West Bengal, India} 
\address{\href{mailto:parthakrde@gmail.com}{parthakrde@gmail.com} \\ 
\href{https://www.linkedin.com/in/parthakrdey/}{https://www.linkedin.com/in/parthakrdey/} \\ \href{https://github.com/Parthadee}{https://github.com/Parthadee} }  

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Aspiring Junior Python Developer eager to leverage strong programming skills in Python, JavaScript, and SQL to build robust web applications. Passionate about creating responsive and user-friendly solutions while continuously learning and growing in a dynamic environment.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Master of Computer Application}, Brainware University\hfill West Bengal, India \\
Percentage: 81.26(8.13/10.0).\hfill {Aug. 2023 -- Present}


{\bf B.Tech. Civil Engineering}, Narula Institute of Technology,MAKAUT\hfill West Bengal, India \\
Percentage: 67.1 (7.46/10.0).\hfill {Aug. 2018 -- July 2021}

{\bf Diploma, Civil Engineering}, Narula Institute of Technology,WBSCTE\hfill West Bengal, India \\
Percentage: 65.6(7.0/10.0).\hfill {Aug. 2015 - Sept. 2018 }

{\bf 10th (Secondary Examination)}, Aditya Academy Senior Secondary, CBSE\hfill West Bengal, India \\
Percentage: 45.5(4.8/10.0).\hfill {Feb. 2013 - May 2014}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{5ex}} l }
Programming Languages: &Python, JavaScript, HTML5, CSS3
\\
Frameworks/Technologies: &jQuery, API, responsive design, SQL,database management\\
Design/Development: &Wireframe layout, UI/UX, back-end, front-end\\
Soft Skills: & Attention to Detail, Time Management, Problem-Solving,  Adaptability \\
Tasks: &Develop applications, design user interfaces, optimize SQL queries
\end{tabular}\\
\end{rSection}   

\begin{rSection}{EXPERIENCE}

\textbf{Intern} \hfill Nov 2024 - Present\\
AWS Intern,WebGuru Infosystems \hfill \textit{West Bengal, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Implemented cloud-based solutions using AWS services to improve system reliability.
    \item Deployed scalable applications on AWS, leading to a 30\% reduction in system errors and a 25\% improvement in performance. 
 \end{itemize}
 
\textbf{Trainee} \hfill Feb. 2022 - Apr. 2023\\
Training and Development Center,Jspider \hfill \textit{Bengaluru, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Achieved 75\% growth for Full stack Development using Java, HTML/CSS, and SQL skills.
    \item Executed new social media strategies, amplifying brand presence and engagement, resulting in a 40\% follower growth 
 \end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Confirm-Booking} {Developed a Laravel-based PHP app for booking PG rooms, renting houses, and listing properties \href{https://github.com/Parthadee/Confirm-booking}{https://github.com/Parthadee/Confirm-booking}}
\item \textbf{E-commerce (Zudio)} {Created a stylish Zudio e-commerce site using WordPress with responsive themes and plugins \href{https://github.com/Parthadee/E-commerces}{https://github.com/Parthadee/E-commerces}}


%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications} 
{\bf Java Full Stack Development} \hfill {\bf Bengaluru, India} \\
Qspider/Jspider\hfill Feb. 2022 - July 2023
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
