\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{PARTHA DEY} \\
 % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{Data Engineer \\ (+91) 9062681888 \\ West Bengal, India} 
\address{\href{mailto:parthakrde@gmail.com}{parthakrde@gmail.com} \\ 
\href{https://www.linkedin.com/in/parthakrdey/}{https://www.linkedin.com/in/parthakrdey/} \\ \href{https://github.com/Parthadee}{https://github.com/Parthadee} }  

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Seeking an entry-level Data Engineering position to kick-start a career in building scalable data pipelines, optimizing ETL processes, and working with technologies skill such as Python, SQL, Spark, and AWS. Committed to \\ supporting organizational goals through innovative solutions, with a strong dedication to continuous improvement in data architecture and engineering best practices. Eager to contribute effectively to the team’s success and add value to the organization through technical and collaborative skills.}


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Master of Computer Application}, Brainware University\hfill West Bengal, India \\
Percentage: 81.26(8.13/10.0).\hfill {Aug. 2023 -- Present}


{\bf Bachelor of Technology in Civil}, Narula Institute of Technology\hfill West Bengal, India \\
Percentage: 67.1 (7.46/10.0).\hfill {Aug. 2018 -- July 2021}
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{5ex}} l }
Programming Languages:  & Java, Python, SQL, JavaScript
\\
Core Skills: & Data Pipelines, ETL, Data Modeling, Data Warehousing, Data Quality\\
Big Data Frameworks:  & Spark, PySpark \\
Additional Skills: &Algorithms and Data Structures, Cloud Platforms: AWS/Azure\\
Development Tools:  & PySpark, Apache Hadoop, Git/GitHub, Visual Studio Code \\
Operating System: & Linux, Windows, macOS \\
Soft Skills: & Strong Communication Skills, Teamwork, Leadership, Emotional intelligence, \\& Adaptability, Problem-Solving, Work ethic 
\end{tabular}\\
\end{rSection}   

\begin{rSection}{EXPERIENCE}

\textbf{Intern} \hfill Nov 2024 - Present\\
WebGuru Infosystems \hfill \textit{West Bengal, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item ReactJS Web Development: Built dynamic interfaces using ReactJS for web applications.
    \item Developed and deployed a software update, resulting in a 30\% reduction in system errors and improving \\ application performance by 25\% 
 \end{itemize}
 
\textbf{Trainee} \hfill Feb. 2022 -- Apr. 2023\\
Training and Development Center(Jspider) \hfill \textit{Bengaluru, India}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Achieved 75\% growth for Full stack Development using Java, HTML/CSS, and SQL skills.
    \item Executed new social media strategies, amplifying brand presence and engagement, resulting in a 40\% follower growth 
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Confirm-Booking} {Developed a Laravel-based PHP app for booking PG rooms, renting houses, and listing properties \href{https://github.com/Parthadee/Confirm-booking}{https://github.com/Parthadee/Confirm-booking}}
\item \textbf{E-commerce (Zudio)} {Created a stylish Zudio e-commerce site using WordPress with responsive themes and plugins \href{https://github.com/Parthadee/E-commerces}{https://github.com/Parthadee/E-commerces}}


%----------------------------------------------------------------------------------------
\begin{rSection}{Certifications} 
{\bf Google Analytics for Beginners} \hfill {\bf West Bengal, India} \\
Google Analytics Academy \hfill Feb. 2022 - July 2024
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
